### 2013-09-16 manuscripts/reply/reply.tex
Adding manuscripts.
Adding `manuscripts` directory and basic latex setup.

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2,3}$ and Mark T.\ Holder$^{2}$

        \bigskip
        $^1$\emph{Biodiversity Institute\\
            $^2$Department of Ecology and Evolutionary Biology\\ 
            University of Kansas\\
            %1345 Jayhawk Blvd\\
            Lawrence, KS 66045\\
            USA}\\[.1in]
        $^3$\emph{Corresponding author} (\href{mailto:joaks1@ku.edu}{\tt
        joaks1@ku.edu})\\

@@

%:FIGURE-accuracy omega SS GLM
\begin{figure}[hbtp]
    \captionsetup{listformat=figList}
    \centering
    \includegraphics[width=1.0\textwidth]{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}
    \caption{
        Model-choice behavior \ldots
    }
    \label{fig_dpp_dpp_val_mc}
\end{figure}

>>>>

        \vspace{12pt}
        Jamie R. Oaks$^{1,2,5}$, Jeet Sukumaran$^{1,2}$, Jacob A.
        Esselstyn$^{3}$, Charles W. Linkem$^{1,2}$, Cameron D.
        Siler$^{4}$, Mark T. Holder$^{2}$ and Rafe M. Brown$^{1,2}$

        \bigskip
        $^1$\emph{Biodiversity Institute\\
            $^2$Department of Ecology and Evolutionary Biology\\ 
            University of Kansas\\
            %1345 Jayhawk Blvd\\
            Lawrence, KS 66045\\
            USA}\\[.1in]
        $^3$\emph{Biology Department\\
            McMaster University\\
            % Life Sciences Building Rm 328\\
            Hamilton, Ontario L8S4K1\\
            Canada}\\[.1in]
        $^4$\emph{Department of Biology\\
            University of South Dakota\\
            Vermillion, SD 57069\\
            USA}\\[.1in]
        $^5$\emph{Corresponding author} (\href{mailto:joaks1@ku.edu}{\tt
        joaks1@ku.edu})\\

@@

%:FIGURE-accuracy omega SS GLM
\begin{figure}[hbtp]
    \captionsetup{listformat=figList}
    \centering
    \includegraphics[width=1.0\textwidth]{../../saturation/saturation-plot.pdf}
    \caption{
        Saturation plot \ldots
    }
    \label{fig_saturation_plot}
\end{figure}
